Age-related changes in plant growth and traits

### 2016-06-20 scripts/Accessory_figs_20160218.Rmd
continued work on figs for ms

acc_by_species$slope2 <- paste(format(acc_by_species$Slope,digits=3)," (",format(acc_by_species$Slope_lowCI,digits=3)," - ",format(acc_by_species$Slope_highCI,digits=3),")",sep="")

@@

write.csv(results, file="figs2/Accessory_Costs/Table06_eacc_cost_vs_seedset_by_spp.csv",row.names=FALSE)
```

@@

write.csv(results, file="figs2/Accessory_Costs/Table07a_accessory_vs_RE.csv",row.names=FALSE)

@@

write.csv(results, file="figs2/Accessory_Costs/Table07b_accessory_vs_total_weight.csv",row.names=FALSE)

@@

write.csv(results, file="figs2/Accessory_Costs/Table07c_accessory_vs_age.csv",row.names=FALSE)
dev.off()
```

>>>>

acc_by_species$slope2 <- paste(format(acc_by_species$Slope,digits=3)," (",format(acc_by_species$Slope_lowCI,digits=3)," ̶ ",format(acc_by_species$Slope_highCI,digits=3),")",sep="")

@@

results$slope2 <- paste(format(results$Slope,digits=3)," (",format(results$Slope_lowCI,digits=3)," ̶ ",format(results$Slope_highCI,digits=3),")",sep="")

results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=2)
results$Slope_test_p <- format(results$Slope_test_p,digits=3)
acc_slopes <- dplyr::select(results,variable,r2,pval,slope2,Slope_test_p)

write.csv(results, file="figs2/Accessory_Costs/Table04_eacc_cost_vs_seedset_by_spp.csv",row.names=FALSE)
```

@@

write.csv(results, file="figs2/Accessory_Costs/Table05a_accessory_vs_RE.csv",row.names=FALSE)

@@

write.csv(results, file="figs2/Accessory_Costs/Table05b_accessory_vs_total_weight.csv",row.names=FALSE)

@@

write.csv(results, file="figs2/Accessory_Costs/Table05c_accessory_vs_age.csv",row.names=FALSE)
dev.off()
```
